Species persistence under climate and fishing

### 2014-02-01 Writing/MS.tex
remade table

\noindent Regardless of the exact functional form of the recruitment function, a critical parameter of the recruitment function in determining population persistence is how quickly recruitment increases when the population 
size is near (but above) $0$, which is equivalent to the intrinsic growth rate, $R_0=f'(0)$.  Analyzing this kind of model becomes easier if the dispersal kernel is separable into its dependence on the source of larvae and its dependence on the destination of the larvae, i.e.~if there are functions $a_i, b_i$ such that $k(x- y) = \sum^\infty_{i=1} a_i(x)b_i(y)$ and we use such a kernel in our analytical expressions. We provide a list of variables and functions in Table 1.

@@

\[k(x-y)=\frac{1}{\sqrt{2\sigma^2\pi}}e^{\frac{-(x-y)^2}{2\sigma^2}}.\]

@@

For each kernel, the population's ability to persist depends on properties of the population itself-- the expected distance a larva disperses ($\langle d \rangle$) and the intrinsic growth rate ($R_0$); properties of the environment-- the length of the viable patch ($L$) and how quickly the environment is shifting ($c$); and the harvesting rate ($h
$).  Whereas equilibrium biomass depends on the function form of recruitment, population persistence only depends on the intrinsic growth rate $R_0$.  If the environment shifts more quickly than the critical rate $c^*$ or the population is harvested at more than 
the critical rate $h^*$ then the population will not be able to persist, as described in the Appendix.  For a Gaussian kernel, the critical rates $c^*$ and $h^*$ are those values of $c$ and $h$ such that 
$$R_0(1-h)2\sqrt{2}\exp\left(\frac{-c^2}{8D}\right)\left[\text{erf}\left(\frac{L-c}{2\sqrt{2D}}\right)-\text{erf}\left(\frac{-L-c}{2\sqrt{2D}}\right)\right]=1.$$
A similar expression for a sinusoidal kernel is derived in the appendix.  For both kernels, the critical harvesting proportion can be approximated by a function that looks like 
\begin{equation}
h^*\sim1- \frac{1}{R_0}\cdot C(L,R_0)f(\sigma^2,c^2,L^2+3c^2),
\end{equation}
where $C(L,R_0)$ is a decreasing function of the length of the viable patch and the intrinsic growth rate.

@@

The equilibrium biomass of the population as a function of the rate of environmental shift on the x-axis and the harvesting rate on the y-axis with and without management strategies.  (a) No management.  (b) Threshold harvesting levels.  (c) MPAs.  These results are from a simulation with a Laplacian dispersal kernel with parameters $L=1$, $R_0=5$, $K=100$, and $\langle d \rangle =2$.

@@

>>>>

\noindent Regardless of the exact functional form of the recruitment function, a critical parameter of the recruitment function in determining population persistence is how quickly recruitment increases when the population 
size is near (but above) $0$, which is equivalent to the intrinsic growth rate, $R_0=f'(0)$.  Analyzing this kind of model becomes easier if the dispersal kernel is separable into its dependence on the source of larvae and its dependence on the destination of the larvae, i.e.~if there are functions $a_i, b_i$ such that $k(x- y) = \sum^\infty_{i=1} a_i(x)b_i(y)$ and we use such a kernel in our analytical expressions. We provide a list of variables and functions in Table \ref{variables}.

@@

\[k(x-y)=\frac{1}{2\sqrt{D\pi}}e^{\frac{-(x-y)^2}{4D}}.\]

@@

For each kernel, the population's ability to persist depends on properties of the population itself-- the expected distance a larva disperses ($\langle d \rangle$) and the intrinsic growth rate ($R_0$); properties of the environment-- the length of the viable patch ($L$) and how quickly the environment is shifting ($c$); and the harvesting rate ($h
$).  Whereas equilibrium biomass depends on the function form of recruitment, population persistence only depends on the intrinsic growth rate $R_0$.  If the environment shifts more quickly than the critical rate $c^*$ or the population is harvested at more than 
the critical rate $h^*$ then the population will not be able to persist, as described in the Appendix.  For a Gaussian kernel, the critical rates $c^*$ and $h^*$ are those values of $c$ and $h$ such that 
$$R_0(1-h)2\sqrt{2}\exp\left(\frac{-c^2}{8D}\right)\left[\text{erf}\left(\frac{L-c}{2\sqrt{2D}}\right)-\text{erf}\left(\frac{-L-c}{2\sqrt{2D}}\right)\right]=1.$$
A similar expression for a sinusoidal kernel is derived in the appendix.  For both kernels, the critical harvesting proportion can be approximated by a function that looks like 
\begin{equation}
h^*\sim1- \frac{1}{R_0}\cdot C(L,R_0)f(\langle d \rangle,c^2,L^2+3c^2),
\end{equation}
where $C(L,R_0)$ is a decreasing function of the length of the viable patch and the intrinsic growth rate.

@@

Figure \ref{management}: The equilibrium biomass of the population as a function of the rate of environmental shift on the x-axis and the harvesting rate on the y-axis with and without management strategies.  (a) No management.  (b) Threshold harvesting levels.  (c) MPAs.  These results are from a simulation with a Laplacian dispersal kernel with parameters $L=1$, $R_0=5$, $K=100$, and $\langle d \rangle =2$.

@@

\section{Tables}

\begin{table}
\begin{tabular}{@{}lllllll@{}}
  Variable & Definition
\\\cmidrule{1-1} \cmidrule{2-2}   
$n_t(x)$ & density of fish at position $x$ at time $t$
\\ $n^*(\overline{x})$ & density of fish at equilibrium at position $\overline{x}$ relative to the patch 
\\ $k(x-y)$ & dispersal kernel, probability of larva traveling from position $y$ to position $x$
\\ $\langle d \rangle $ & expected distance traveled by larva
\\ $f(n)$ & recruitment function, number of offspring produced by a population of size $n$
\\ $R_0$ & intrinsic growth rate, $R_0=f'(0)$
\\ $h$ & proportion of adults harvested
\\ $L$ & patch length
\\ $c$ & rate of environmental shift
\end{tabular}
\caption{}
\label{variables}
\end{table}
